%-------------------------
% Resume in Latex
% Author : Jonathan Oktaviano Frizzy
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Jonathan Oktaviano Frizzy} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:081357473781}{+62 813 5747 3781}
    $|$
    \faAt \hspace{.5pt} \href{mailto:jonathanoktavianofrizzy@gmail.com}{jonathanoktavianofrizzy@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://linkedin.com/in/jonathan-oktaviano/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/robotjaol}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://robotjaol.vercel.app/}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/3KcJKWS8gMk1GiZMA}{Surabaya, Indonesia}
\end{center}

%----------- EDUCATION -----------

% \section{Education}
%   \vspace{3pt}
%   \resumeSubHeadingListStart
    
%     \resumeEducationHeading
%       {Institut Teknologi Sepuluh Nopember}{Surabaya, Indonesia}
%       {1nd Year in Electrical Automation Engineering; \textbf{GPA: 3.49/4.00}}{Jul 2022 \textbf{--} Apr 2023}
      
    
  
%   \resumeSubHeadingListEnd

 \section{Education}
   \vspace{3pt} 
    \resumeSubHeadingListStart

       \resumeEducationHeading
         {Institut Teknologi Sepuluh Nopember}
         {Surabaya, Indonesia}
         {2nd Year in Electrical Automation Engineering}
         {GPA: 3.49/4.00}
         {Jul 2022 -- Present}
  
    \resumeSubHeadingListEnd


%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ C/C++, C\#, Python, JavaScript, PHP, LabVIEW, MATLAB} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Flask, Streamlit, Node.js, React.js, Git, AWS, RabbitMQ, OpenCV, PyTorch, Mediapipe, TensorFlow, Arduino, ESP32, STM32, PLC Omron, PLC Mitsubishi, ROS} \\ \vspace{3pt}
        
        \textbf{Methodologies:} {OOP, Functional Programming} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Chico Service Electronic}{Tulungagung, Indonesia}
      {Electronic Engineer}{July 2021 \textbf{--} Dec 2021, Full-time}
        \resumeItemListStart
            \resumeItem{Designing a PCB for a DIY audio driver assembly using Autodesk Fusion 360/Eagle software, employing manual printing, followed by conducting test trials on the audio driver.}
            \resumeItem{Designing a custom Power Supply and Amplifier box utilizing an external audio driver, custom 10A power supply, and polarity protection circuitry.}
            \resumeItem{Designing a mini power supply or mini adapter complete with a casing box.}
            \resumeItem{Performing troubleshooting and repairs on electronic devices such as Television, electric fans, power outlets, sound mixer, and remote controls.}
        \resumeItemListEnd

    \resumeSubheading
      {SMAN 1 Durenan}{Trenggalek, Indonesia}
      {Teaching Assistant}{Jan 2022 \textbf{--} Feb 2022, Part-time}
        \resumeItemListStart
            \resumeItem{Delivering instruction on the fundamentals of electrical circuits theory based on the laws of physics, followed by hands-on guidance in assembling basic electrical circuits such as series and parallel, alongside introducing various DC and AC electronic components.}
            \resumeItem{Instructing foundational algorithms and programming principles using the C language, subsequently applied to microcontrollers for creating simple projects employing components like LEDs, HC-SR04 sensors, and others.}
            \resumeItem{Providing instruction on constructing both analog and microcontroller-based line tracer robots, offering practical exercises and operational guidance}
        \resumeItemListEnd


    \resumeSubheading
      {Digitalent KOMINFO}{Surabaya, Indonesia}
      {Teaching Assistant}{Jan 2023 \textbf{--} Jun 2023, Part-time}
        \resumeItemListStart
            \resumeItem{Working on and evaluating the code submitted by participants Junior Website Developer.}
            \resumeItem{Compiling attendance data for each session.}
            \resumeItem{Conducting tests on each participant's Final Project, and then assigning assessment points to each feature of the projects submitted by the participants}
        \resumeItemListEnd
    

    \vspace{2pt}
    \resumeSubheading
      {KKN Tematik Institut Teknologi Sepuluh Nopember}{Surabaya\textbf{--}Sidoarjo, Indonesia}
      {Leader}{Aug 2023 \textbf{--} Oct 2023, Part-time}
        \resumeItemListStart
            \resumeItem{Fully responsible as the project manager, overseeing the timeline, finances, and logistics in constructing the  \href{https://www.its.ac.id/news/2023/09/12/bantu-petambak-abmas-its-gagas-alat-pengontrol-kualitas-air/}{\color{blue}Smart Integrated Water Quality Monitoring System project}.}
            \resumeItem{Creating a monitoring device website using PHP to store data from all sensors of the device, accessible from anywhere.}
            \resumeItem{Designing the installation scheme of electronic hardware components for the project, comprising sensing components, actuators, and radio transmitters.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Autonomy Challenge at International Roboboat Competition}{ Secured 3rd place by integrating and coordinating all electronic components in 'Nala Proteus V.2,' including PCB, sensors, and actuators. Developed electrical and communication architecture, implemented with a success rate of 90 percent {(Feb 2024)} \\ \vspace{3pt}
        
        \textbf{Autonomy Challenge at International Roboboat Competition}{ 1st place, Working on and combining all electronic devices in "Nala Proteus" such as PCB and others.Designing electrical architecture and battery managament. {(Mar 2023)} \\ \vspace{3pt}
        
        \textbf{Autonomous Tourism Surface Vehicle Prototype Contest, Kontes Kapal Cepat Tak Berawak (KKCTBN)}{ Secured the 1st place by Took part in helping on developing electrical systems for Barunastra ITS' "Nala Athena" Autonomous Tourism Surface Vehicle Prototype Ship. (Oct 2023)} \\ \vspace{3pt}
        
        \textbf{LKS Nasional Mobile Robotic}{ Secured the 3rd place by creating a robot utilizing a National Instruments controller, MyRIO, integrated with actuators such as servos and PG motors, and featuring a camera for barcode, color, and obstacle detection, serving as a hospital service robot (Oct 2022)} \\ \vspace{3pt}
        
        \textbf{SMK Sore Tulungagung Award:}{ Graduated as the highest ranked student. (Jun 2022)}
    }}}}
\resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Portofolio Webiste} $|$ \emph{\href{https://robotjaol.vercel.app/}{\color{blue}Website}}}{}
          \resumeItemListStart
            \resumeItem{For this project, I created a portfolio website using semantic HTML and SCSS. The HTML provides a clear and meaningful structure, while the SCSS ensures a cohesive and visually appealing design. This website effectively showcases my skills in web development and branding.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{STM32 Training Kit} $|$ \emph{\href{https://github.com/robotjaol/STM32_Training_Kit}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{I meticulously engineered this microcontroller utilizing the STM32F103C8T6 IC, ensuring a precise and tailored design to meet the specific requirements of the project. I employed KiCAD software for the schematic capture and PCB layout, which allowed for a highly detailed and efficient design process. This comprehensive approach resulted in the creation of the STM32 Training Kit for Barunastra ITS, aimed at providing a robust and versatile training tool. The kit is designed to facilitate hands-on learning and experimentation, equipping users with practical experience in microcontroller programming and system development.}
          \resumeItemListEnd
          
     \resumeProjectHeading
        {\textbf{Electric Vehicle Sensor Monitoring} $|$ \emph{\href{https://github.com/robotjaol/esp32_breakout_board}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{In this project, I developed a custom PCB for an ESP32 microcontroller, which is equipped with an embedded CAN bus module. The design and implementation were specifically tailored to meet the needs of electric vehicle monitoring. This custom PCB enables efficient communication and data transmission within the vehicle's network, ensuring real-time monitoring and control. The project showcases my ability to design specialized hardware solutions for advanced applications in the automotive industry.}
          \resumeItemListEnd
          
      \resumeProjectHeading
        {\textbf{Smart Integrated Water Quality Monitoring System} $|$ \emph{\href{https://github.com/robotjaol/kkn_project}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{This project was part of my Community Empowerment Program (KKN), with a focus on thematic environmental issues. The primary goal was to monitor the water quality of ponds by measuring key parameters such as temperature, pH, and oxygen levels. To facilitate the analysis and sharing of this data, I also developed a website to store and display all the collected information. This project aimed to provide valuable insights into the environmental health of local water bodies and support efforts in maintaining and improving water quality.}
          \resumeItemListEnd

     \resumeProjectHeading
        {\textbf{CCTV Thermal HVAC} $|$ \emph{\href{https://github.com/robotjaol/thermal_CCTV_HVAC}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{In this project, I integrated an environmental thermal detection system using Thermal CCTV with an HVAC cooling system to enhance energy efficiency. The system automatically cools the room based on temperature readings from the Thermal CCTV. Additionally, I created a universal remote to control the HVAC system. I used Python and C for programming and developed a monitoring website. Key technologies included YOLO for object detection and Flask for web development.}
          \resumeItemListEnd
          
     \resumeProjectHeading
        {\textbf{Oil Navigating Ship} $|$ \emph{\href{https://www.linkedin.com/in/jonathan-oktaviano/C}{\color{blue}LinkedIn}}}{}
          \resumeItemListStart
            \resumeItem{In this project, I assumed the dual role of an electrical and mechanical conceptor and consultant. My duties encompassed the design of electrical and communication diagrams for the ship, ensuring comprehensive and efficient systems integration. Additionally, I provided valuable recommendations for implementing ship maneuvers, contributing to the overall functionality and safety of the vessel. My multifaceted involvement underscores my expertise in both electrical and mechanical engineering disciplines, as well as my capacity to offer strategic insights across various aspects of maritime engineering projects.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}

%         \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
%     }}
%   \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

\section{Certificates}
\resumeSubHeadingListStart
    \resumeOrganizationHeading
      {Project Manager by Google}{Mar 2024}{Foundation Project Management \href{https://www.coursera.org/account/accomplishments/verify/FUGNKUSUYHBA}{\color{blue}Certificate}.}

    \resumeOrganizationHeading
      {Artificial Intelligence for Business by NASBA}{Mar 2024}{Introduction to Artificial Intelligence \href{https://www.linkedin.com/in/jonathan-oktaviano/details/certifications/1710528282367/single-media-viewer/?profileId=ACoAAEB2k00Bw-v1yxcDJJYIGidC5SNJ_jZ5UHg}{\color{blue}Certificate}.}

    \resumeOrganizationHeading
      {Front-end Website Developer by Dicoding Indonesia}{Mar 2024}{The front-end website utilized Bootstrap and JavaScript for enhanced interactivity. \href{https://www.dicoding.com/certificates/JLX12NYLJZ72}{\color{blue}Certificate}.}

  \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

\section{Organizations}
  \resumeSubHeadingListStart

    \resumeOrganizationHeading
      {Barunastra ITS}{Dec 2022 -- Present}{Staff Electrical Division}

    \resumeOrganizationHeading
      {UKM Robotika ITS}{Oct 2022 -- Present}{Member}

  \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Basketball, Swimming, Fitness, Eight-ball, Horology}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}